Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-19 paper/paper.tex

%% Чтобы переключиться на русский язык в некоторых секциях, можно 
%% раскомментировать следующие две команды
% \renewcommand{\texten}[1]{}
% \renewcommand{\textru}[1]{\foreignlanguage{russian}{\emph{#1}}{}}

@@

\texten{
For memory-tight applications such as embedded systems it can be useful to
utilise the suggested condensation in a lazy way, so that without actually
constructing the condensed image we use a function (``view'') calculating color of
each cell with 4 lookups to the original binary image.
This is probably most interesting when combined with SUF2 algorithm, as it is a way
to win some time while avoiding memory footprint increase.
However this lazy approach increases the number of image lookups.
% So, according to our benchmark, this combination is efficient only for dense
% ($>30\%$) noise.
}\textru{
В некоторых случаях может быть более приемлемо использовать сжатие неявно, то
есть вместо построения 
}

@@

Line charts with benchmarks of mentioned algorithms on different noise images
are shown on
\Cref{fig:overall:times}.

@@

\begin{figure}
  \centering
  \includegraphics[height=0.45\textheight, keepaspectratio]{pics/overall.eps}
  \caption{Average CPU time per run on random images $1200 \times 1800$ px.}
  \label{fig:overall:times}
\end{figure}

\newcommand{\inputnorm}[1]{
  \begin{subfigure}[t]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth,
                     keepaspectratio]{pics/normed_#1.eps}
    \caption{Some.}
    \label{fig:normed:#1}
  \end{subfigure}
}

\begin{figure}
  \centering
  \inputnorm{DFS}
  \inputnorm{SUF}
  \inputnorm{SUF2}
  \inputnorm{DTSUF}
  \label{fig:normed}
\end{figure}

>>>>

%% Чтобы переключиться на русский язык в некоторых секциях, можно 
%% раскомментировать следующие две команды
\renewcommand{\texten}[1]{}
\renewcommand{\textru}[1]{\foreignlanguage{russian}{\emph{#1}}{}}

@@

For memory-tight applications such as embedded systems it can be useful to
utilise the suggested condensation in a lazy way, so that without actually
constructing the condensed image we use a function (``view'') calculating color of
each cell with 4 lookups to the original binary image.
This is probably most interesting when combined with SUF2 algorithm, as it is a way
to win some time while avoiding memory footprint increase.
However this lazy approach increases the number of image lookups.
% So, according to our benchmark, this combination is efficient only for dense
% ($>30\%$) noise.

@@

Line charts with benchmarks of mentioned algorithms on different noise images are shown on
\Cref{fig:noise400x600,fig:noise800x1200,fig:noise1200x1800,fig:noise2000x3000,fig:noise4000x6000}.

@@

\newcommand{\inputtable}[2]{
  \begin{figure}
    \centering
    \includegraphics[height=0.45\textheight, keepaspectratio]{pics/#1x#2.eps}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px.}
    \label{fig:noise#1x#2}
  \end{figure}
 % \begin{table}[p]
 %   \centering
 %   \input{tables/#1x#2}
 %   \caption{Average CPU time per run on noise images $#1 \times #2$ px}
 %   \label{tab:noise#1x#2}
 % \end{table}
}

% \inputtable{200}{300}
\inputtable{400}{600}
\inputtable{800}{1200}
\inputtable{1200}{1800}
\inputtable{2000}{3000}
\inputtable{4000}{6000}
% \inputtable{5000}{7500}
